### 2015-03-19 evaluation.tex
updated table

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table*}[t]
\small
\centering
\begin{tabular}{l rrr rr rr r r}
\centering
\input{experiments/tables/granularity.tex}
\end{tabular}
\caption{Results ...}
\label{tab:races}
\end{table*}

@@

>>>>

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table*}[t]
\small
\centering
\begin{tabular}{l rrr rrr rr r r}
\centering
\input{experiments/tables/granularity.tex}
\end{tabular}
\caption{Data race analysis and scalability results.}
\label{tab:races}
\end{table*}

@@

All reported times are in seconds and averages of N executions. We report: lines of C code (LoC); number of entry point pairs (\#Pairs); memory regions in the program (\#MRs); the number of racy memory regions that \whoop found (\#Racy MRs); the number of race reports that \whoop generated (\#Race Reports); the number of races that \corral found (same in all configurations).
